WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-13 paper/ms.tex
recomputed stellar/planet properties w/ TESS data
specifically, the TESS phase-folded LC

Having defined the free and fixed parameters, we calculated an initial
guess for the free parameters by maximizing the likelihood.  We then
sampled over the posterior using the algorithm proposed by
\citet{goodman_ensemble_2010} and implemented by
\citet{foreman-mackey_emcee_2013}.
Table~1 gives the results, which are in reasonable agreement with the
parameters reported by \citet{gillon_improved_2009},
\citet{southworth_high-precision_2009}, and
\citet{huitson_gemini_2017}.
%TODO: is this true? Or do the periods actually differ?

@@

\tablehead{
\colhead{Parameter} & \colhead{Value} & \colhead{Uncertainty} & \colhead{Comment}
}

\startdata
%TODO numbers with updated method
{\it Transit/RV parameters:} & & & \\
  $R_{\rm p}/R_\star$                        & $0.XXXX$               & $\pm 0.0013$                & A \\
  $i$~[deg]                                  & $XX.XX$                & $+0.39$, $-0.26$            & A \\
  $a/R_\star$                                & $5.XXX$                & $+0.025$, $-0.020$          & A \\
  $u_{\rm linear}$                           & $0.XXX$                & $+0.XXX$, $-0.XXX$          & A \\
  $u_{\rm quad}$                             & $0.XXX$                & $+0.XXX$, $-0.XXX$          & A \\
  $K$~[m~s$^{-1}$]                           & $241.1$                & $+2.8$, $-3.1$              & B \\
{\it Stellar parameters:} & & & \\
  $T_{\rm eff}$~[K]                          & $5400$                 & $\pm 90$                    & C \\
  $\log g_\star$~[cgs]                       & $4.47$                 & $\pm 0.11$                  & C \\
  $[{\rm Fe/H}]$                             & $-0.07$                & $\pm 0.19$                  & C \\
  $F_{\rm bol}$~[erg~cm$^{-2}$~s$^{-1}$]     & $2.802\times10^{-10}$  & $\pm 0.076\times10^{-10}$   & D \\
  $\pi$~[mas]                                & $3.7145$               & $0.0517$                    & F \\
  $R_\star$~[R$_{\odot}$]                    & $0.893$                & $\pm 0.034$                 & E \\
  $\rho_\star$~[g~cm$^{-3}$]                 & $1.722$                & $+0.024$, $-0.019$          & E \\
  $M_\star$~[M$_{\odot}$]                    & $0.870$                & $+0.085$, $-0.077$          & E \\
  $T$ magnitude                              & $11.778$               & $\pm 0.018$                 & G \\
{\it Planetary parameters:} & & & \\
  $a$~[AU]                                   & $0.0227$               & $\pm 0.0007$                & E \\
  $M_p$~[M$_{\rm Jup}$]                      & $1.192$                & $+0.091$, $-0.086$          & E \\
  $R_p$~[R$_{\rm Jup}$]                      & $1.337$                & $\pm 0.048$                 & E \\
\enddata

\tablecomments{
  (A) From TESS lightcurves (\S~\ref{sec:measurement}). Orbital periods from timing data are in Table~4.
  (B) \citep{triaud_spin-orbit_2010}.
  (C) From HARPS spectra \citep{doyle_accurate_2013}.
  (D) \citet{stassun_accurate_2017}.
  (E) From functions of stellar, transit or RV parameters as discussed in text.
  (F) {\it Gaia} DR2.
  (G) \citet{stassun_TIC_2018}.
}

@@

We list the resulting parameters in Table~3, and adopt them for the
remaining analysis.  Our parameters broadly agree with those of
previous authors
\citep{wilson_wasp-4b_2008,gillon_discovery_2009,winn_transit_2009,southworth_homogeneous_2011,petrucci_no_2013}.
Comparing our empirical result with the Yonsei-Yale evolutionary track
predicted by the spectroscopic parameters, we see that WASP-4 has an
age $\approx 7\,{\rm Gyr}$, and is securely in the main-sequence stage
of evolution.

@@

There were fewer available occultation times.
\citet{beerer_secondary_2011} observed two occultations of WASP-4b
using warm Spitzer in the 3.6\,$\mu$m and 4.5\,$\mu$m bands.
\citet{caceres_ground-based_2011} detected an occultation from the
ground in the $K_S$ band, and gave a time in HJD, without
specifying the time standard.  We assumed the standard was UTC, but
added $32.182 + N$ seconds of uncertainty to the reported errors,
where $N=35$ is the appropriate number of leap-seconds
\citep{eastman_achieving_2010}.
Though not rigorous, this procedure inflated the error bar to a more
realistic $\pm$94 seconds.
%Finally, as previously mentioned, \citet{ranjan_atmospheric_2014}
%acquired occultation data with HST but kept the epoch as a fixed
%parameter.
Finally, \citet{zhou_secondary_2015} acquired occultation data from
the Anglo-Australian Telescope, focusing on the eclipse depth, but
also fitting for $e\cos\omega$.  We converted their reported
$e\cos\omega$ to a midtime, using their ephemeris and the standard
formula \citep[{\it e.g.},][]{winn_exoplanet_2010}
\begin{equation}
  t_{\rm occ}(E) =
  t_0 +  P E  +
  \frac{P}{2} \left( 1 + \frac{4}{\pi} e\cos\omega \right).
  \label{eq:occultation_time}
\end{equation}
In total, we had four occultations.  Although the occultation times
were less precise than the transit times, they nonetheless helped 
modeling the timing variations.

>>>>

Having defined the free and fixed parameters, we calculated an initial
guess for the free parameters by maximizing the likelihood.  We then
sampled over the posterior using the algorithm proposed by
\citet{goodman_ensemble_2010} and implemented by
\citet{foreman-mackey_emcee_2013}.
Table~1 gives the results, which are in reasonable agreement with the
parameters reported by \citet{gillon_improved_2009},
\citet{southworth_high-precision_2009}, and
\citet{huitson_gemini_2017}.

@@

\tablehead{
\colhead{Parameter} & \colhead{Value} & \colhead{68\% Confidence Interval} & \colhead{Comment}
}

\startdata
{\it Transit/RV parameters:} & & & \\
  $R_{\rm p}/R_\star$                        & $0.15117$              & $+0.00047$, $-0.00037$      & A \\
  $i$~[deg]                                  & $88.85$                & $+0.77$, $-0.90$            & A \\
  $a/R_\star$                                & $5.457$                & $+0.030$, $-0.066$          & A \\
  $u_{\rm linear}$                           & $0.388$                & ---                         & A \\
  $u_{\rm quad}$                             & $0.212$                & ---                         & A \\
  $K$~[m~s$^{-1}$]                           & $241.1$                & $+2.8$, $-3.1$              & B \\
{\it Stellar parameters:} & & & \\
  $T_{\rm eff}$~[K]                          & $5400$                 & $\pm 90$                    & C \\
  $\log g_\star$~[cgs]                       & $4.47$                 & $\pm 0.11$                  & C \\
  $[{\rm Fe/H}]$                             & $-0.07$                & $\pm 0.19$                  & C \\
  $F_{\rm bol}$~[erg~cm$^{-2}$~s$^{-1}$]     & $2.802\times10^{-10}$  & $\pm 0.076\times10^{-10}$   & D \\
  $\pi$~[mas]                                & $3.7145$               & $0.0517$                    & F \\
  $R_\star$~[R$_{\odot}$]                    & $0.893$                & $\pm 0.034$                 & E \\
  $\rho_\star$~[g~cm$^{-3}$]                 & $1.717$                & $+0.029$, $-0.062$          & E \\
  $M_\star$~[M$_{\odot}$]                    & $0.867$                & $+0.087$, $-0.097$          & E \\
  $T$ magnitude                              & $11.778$               & $\pm 0.018$                 & G \\
{\it Planetary parameters:} & & & \\
  $a$~[AU]                                   & $0.0227$               & $\pm 0.0008$                & E \\
  $M_p$~[M$_{\rm Jup}$]                      & $1.189$                & $+0.093$, $-0.104$          & E \\
  $R_p$~[R$_{\rm Jup}$]                      & $1.314$                & $\pm 0.039$                 & E \\
\enddata

\tablecomments{
  (A) From phase-folded TESS lightcurve (\S~\ref{sec:measurement}).
  Orbital periods are in Table~4. The limb darkening parameters were
  allowed to float around the \citet{claret_limb_2017} prediction, but
  were unconstrained.
  (B) \citep{triaud_spin-orbit_2010}.
  (C) From HARPS spectra \citep{doyle_accurate_2013}.
  (D) \citet{stassun_accurate_2017}.
  (E) From functions of stellar, transit or RV parameters as discussed in text.
  (F) {\it Gaia} DR2.
  (G) \citet{stassun_TIC_2018}.
}

@@

We list the resulting parameters in Table~3, and adopt them for the
remaining analysis.  Our parameters broadly agree with those of previous
authors
\citep{wilson_wasp-4b_2008,gillon_discovery_2009,winn_transit_2009,southworth_homogeneous_2011,petrucci_no_2013}.
% The sole exception is that our measured $R_{\rm p}/R_\star$ value is
% slightly smaller than most ground-based measurements (see Tables 2 and
% 3 of \citealt{hoyer_tramos_2013}).  However, looking at the I-band
% measurements of \citet{hoyer_tramos_2013} and taking the mean + std
% deviation, it's a ~1 sigma effect. So I won't mention it!
Comparing our empirical result with the Yonsei-Yale evolutionary track
predicted by the spectroscopic parameters, we see that WASP-4 has an
age $\approx 7\,{\rm Gyr}$, and is securely in the main-sequence stage
of evolution.

@@

There were fewer available occultation times.
\citet{beerer_secondary_2011} observed two occultations of WASP-4b
using warm Spitzer in the 3.6\,$\mu$m and 4.5\,$\mu$m bands.
\citet{caceres_ground-based_2011} detected an occultation from the
ground in the $K_S$ band, and gave a time in HJD, without specifying
the time standard.  We assumed the standard was UTC, and verified that
assuming TDB did not alter any of our conclusions.
%Finally, as previously mentioned, \citet{ranjan_atmospheric_2014}
%acquired occultation data with HST but kept the epoch as a fixed
%parameter.
Finally, \citet{zhou_secondary_2015} acquired occultation data from
the Anglo-Australian Telescope, focusing on the eclipse depth, but
also fitting for $e\cos\omega$.  We converted their reported
$e\cos\omega$ to a midtime, using their ephemeris and the standard
formula \citep[{\it e.g.},][]{winn_exoplanet_2010}
\begin{equation}
  t_{\rm occ}(E) =
  t_0 +  P E  +
  \frac{P}{2} \left( 1 + \frac{4}{\pi} e\cos\omega \right).
  \label{eq:occultation_time}
\end{equation}
In total, we had four occultations.  Although the occultation times
were less precise than the transit times, they nonetheless helped 
modeling the timing variations.
